### 2014-09-25 LaTeX/RhodiumEmp.tex
edits

\begin{itemize}
	\item Conflict intensity
	\item Ln(Conflict Area)
	\item Civil Conflict Type (e.g., territory or non-territory dispute)
	\item Conflict Duration (Years)
\end{itemize}

@@

To estimate the model we use random effects clustered on countries and years. Results using a fixed effects estimation approach are similar.\footnote{The fixed effects model includes the same regressors as the random effects model but adds indicator variables for each country in the sample.}  The model we estimate is shown below:

\begin{align*}
	\% \Delta GDP_{i,t} &= \beta_{1}(Upper \; Income_{i,t}) \\
	& \;+\; \beta_{2}(Conflict \; Intensity_{i,t}) \;+\; \beta_{3}(Ln(Conflict \; Area)_{i,t}) \\
	& \;+\; \beta_{4}(Ln(Min. \; Conflict \; Dist.)_{i,t}) \;+\; \beta_{5}(Conflict \; Type_{i,t}) \\
	& \;+\; \beta_{6}(Conflict \; Duration_{i,t}) \;+\; \beta_{7}(Inflation_{i,t-1}) \\
	& \;+\; \beta_{8}(Ln(Land \; Area)_{i,t}) \;+\; \alpha_{i} + \gamma_{t} + \mu_{i,t}
\end{align*}

>>>>

% Replace list with sentences

% \begin{itemize}
% 	\item Conflict intensity
% 	\item Ln(Conflict Area)
% 	\item Civil Conflict Type (e.g., territory or non-territory dispute)
% 	\item Conflict Duration (Years)
% \end{itemize}

@@

To estimate the model we use random effects clustered on countries. Results using a fixed effects estimation approach are similar.\footnote{The fixed effects model includes the same regressors as the random effects model but adds indicator variables for each country in the sample.} The model we estimate is shown below:

Add in descriptors for each of these variables and expectations of their sign.

\begin{align*}
	\% \Delta Log(GDP_{i,t}) &= \beta_{1}(Ln(Min. \; Conflict \; Dist.)_{i,t}) \\
	& \;+\; \beta_{2}(Conflict \; Intensity_{i,t}) \;+\; \beta_{3}(Conflict \; Type_{i,t}) \\
	& \;+\; \beta_{4}(Conflict \; Duration_{i,t}) \;+\; \beta_{5}(Ln(Conflict \; Area)_{i,t}) \\	
	& \;+\; \beta_{6}(Upper \; Income_{i,t}) \;+\; \beta_{7}(Inflation_{i,t-1}) \\
	&  \;+\; \beta_{8}(Democracy_{i,t-1}) \;+\; \beta_{9}(World \; GDP \; Growth_{t}) \\
	& \;+\; \alpha_{i} + \mu_{i,t}
\end{align*}
